---
title: "ML assignment 1"
author: "Ronae McLin rkm2147"
date: "1/12/2021"
output: github_document
---

```{r}
library(tidyverse)
library(haven)
library(table1)
```

read in the file
```{r}
data_df = read_csv("data.csv")
```

clean data
```{r}
data_df = data_df %>% janitor::clean_names()
```

1. Construct a table providing summaries of the quantitative features of the dataset.Summaries should include the mean, median, minimum value, and maximum value. If you are unable to construct a formatted table within R, you can print raw output, but then comment the output to identify the answer that was requested.
 
 **classification variable was not included in this table**
 #no missing data or values to omit
 
```{r}
table_data = 
table1(~ age + bmi + glucose + insulin + homa + leptin + adiponectin + resistin + mcp_1, data = data_df)
```
 
```{r}
table_data
```

2. Recode BMI into the WHO-defined categories below
Severely underweight - BMI less than 16.5kg/m^2
Underweight - BMI under 18.5 kg/m^2
Normal weight - BMI greater than or equal to 18.5 to 24.9 kg/m^2
Overweight – BMI greater than or equal to 25 to 29.9 kg/m^2
Obesity class I – BMI 30 to 34.9 kg/m^2
Obesity class II – BMI 35 to 39.9 kg/m^2
Obesity class III – BMI greater than or equal to 40 kg/m^2
 
```{r}

```
 
3.Create a bar chart showing the proportion of breast cancer cases and controls within each BMI category

```{r}

```

 
4. Construct a logistic regression model using breast cancer classification as the outcome and glucose, HOMA, leptin, BMI (continuous) and age as the independent variables. Fill in the beta estimate and 95% confidence interval associated with a 1-unit change in HOMA

```{r}

```

 
5.Construct a linear regression model using insulin as the outcome and BMI
(continuous), age, and glucose as the independent variables.
Fill in the beta estimate and 95% confidence interval associated with a 1-unit change in age.


```{r}

```

